The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-06-14 analysis/paper/paper.qmd
Update cache chunk
If the raw data or metadata changes, it should not be taken from cache.

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)
  write_csv(emu_theses, data_path)
} else {
  emu_theses <- read_csv(data_path)
}

>>>>

if (!file.exists(data_path)) {
  # On the first run, this function might take extra time as a Python environment needs to be set up
  emu_theses$text <- convert_pdf_text(pdf_paths)
  write_csv(emu_theses, data_path)
} else {
  emu_theses$text <- read_csv(data_path)$text
}
